### 2015-12-01 paper/4-performance.tex
tried to move a few pictures into their proper place, latex still thinks it knows better where to put them.

%TODO say that you will now prove your claims about the aproach having nearly no impact
%TODO and potentially even claim that you are faster than adevs for some situations, due to the algorithms from PythonPDEVS and further features
%TODO briefly give some hardware info on the machine (CPU, OS, RAM), used software (version of adevs, GCC, ...), and about number of samples/variance
\subsection{Sequential Simulation}
%TODO we start with sequential simulation results, because this is still base case
%TODO compare CPU time with adevs for some benchmarks
%TODO and explain why there is such a difference
%TODO (spend some time here, as this is also important)
\subsubsection{CPU Usage}
%TODO !!! benchmarks are in integers
\paragraph*{Devstone}
The Devstone \cite{DEVStone} benchmark is highly hierarchical, using Direct connection the dxex kernels can exploit this, whereas adevs needs to walk the structure of the model to pass events.
% TODO plot here
\paragraph*{PHold}
PHold \cite{PHOLD} is a parallel oriented benchmark, sequential runtime is measured only as a baseline. The usage of random nr generators takes up a significant amount of runtime in this model.
% TODO plot here
\paragraph*{Interconnect}
Interconnect \cite{van2013research} is a benchmark where all models broadcast, creating a complete graph in terms of dependencies between models. It highlights in sequential simulation the cost of heap allocation (messages) in dxex. As the model count increases, we see the expected quadratic increase in runtime in both kernels, but an increasing penalty for dxex w.r.t. adevs. This effect is due to the heap allocation of the messages by dxex, even though this is minimized using memory pools it remains significant.
% TODO plot here

@@

The flattened models are allocated to kernels by giving each kernel a distinct section of the chain, resulting in a low ratio of inter-kernel to intra-kernel messages. For optimistic, this can cause more reverts since the kernels will start to drift faster as the modelcount increases. Furthermore, optimistic is quite sensitive to an increase in kernels, since the delay before a revert propagates increases. Of note as well is the warm-up time this benchmark requires, for $n=d\times w$ models, it takes $\textup{timeadvance}()*n$ transitions to activate the last model in the chain. For parallel this can be reduced to $\frac{ta()*n}{kernels}$ before the last kernel becomes active.

@@

In Phold \cite{PHOLD} allocation is specified in the benchmark itself, each kernel manages a single node with a constant set of sub-nodes. The parameter R determines the percentage of remote destination models.\\

@@

@@

\paragraph*{Priority Network}
The priority network model is detailed in section 4.4.
\begin{table}[lhtb]
	\centering
	\caption{Priority model n 16, m 9, p 10,  t5e5, unit MiB, 2 kernels}
	\label{pmod_mem}
	\begin{tabular}{| l | l | l |}
		\hline
		DX &DXCon &DXOpt\\ \hline
		35 & 58 &69\\ \hline
	\end{tabular}
\end{table}

>>>>

%TODO say that you will now prove your claims about the aproach having nearly no impact
%TODO and potentially even claim that you are faster than adevs for some situations, due to the algorithms from PythonPDEVS and further features
%TODO briefly give some hardware info on the machine (CPU, OS, RAM), used software (version of adevs, GCC, ...), and about number of samples/variance
\subsection{Sequential Simulation}
%TODO we start with sequential simulation results, because this is still base case
%TODO compare CPU time with adevs for some benchmarks
%TODO and explain why there is such a difference
%TODO (spend some time here, as this is also important)
%\subsubsection{CPU Usage}
%TODO !!! benchmarks are in integers
\subsubsection{Devstone}
The Devstone \cite{DEVStone} benchmark is highly hierarchical, using Direct connection the dxex kernels can exploit this, whereas adevs needs to walk the structure of the model to pass events.\\
\begin{figure}[h]
	\includegraphics[width=.5\textwidth]{fig/fig1.eps}
	\label{fig1.eps}
\end{figure}

\subsubsection{PHold}
PHold \cite{PHOLD} is a parallel oriented benchmark, sequential runtime is measured only as a baseline. The usage of random nr generators takes up a significant amount of runtime in this model.

\subsubsection{Interconnect}
Interconnect \cite{van2013research} is a benchmark where all models broadcast, creating a complete graph in terms of dependencies between models. It highlights in sequential simulation the cost of heap allocation (messages) in dxex. As the model count increases, we see the expected quadratic increase in runtime in both kernels, but an increasing penalty for dxex w.r.t. adevs. This effect is due to the heap allocation of the messages by dxex, even though this is minimized using memory pools it remains significant.\\
\begin{figure}[h]
	\includegraphics[width=.5\textwidth]{fig/fig3.eps}
	\label{fig3.eps}
\end{figure}

@@

The flattened models are allocated to kernels by giving each kernel a distinct section of the chain, resulting in a low ratio of inter-kernel to intra-kernel messages. For optimistic, this can cause more reverts since the kernels will start to drift faster as the modelcount increases. Furthermore, optimistic is quite sensitive to an increase in kernels, since the delay before a revert propagates increases. Of note as well is the warm-up time this benchmark requires, for $n=d\times w$ models, it takes $\textup{timeadvance}()*n$ transitions to activate the last model in the chain. For parallel this can be reduced to $\frac{ta()*n}{kernels}$ before the last kernel becomes active.\\
\begin{figure}[h]
	\includegraphics[width=.5\textwidth]{fig/fig2.eps}
	\label{fig2.eps}
\end{figure}

@@

In Phold \cite{PHOLD}, allocation is specified in the benchmark itself. Each kernel manages a single node with a constant set of sub-nodes. The parameter R determines the percentage of remote destination models.\\

@@

\begin{figure}[h]
	\includegraphics[width=.5\textwidth]{fig/fig4.eps}
	\label{fig4.eps}
\end{figure}

@@

\paragraph*{Priority Network}
The priority network model is detailed in section 4.1.
\begin{table}[lhtb]
	\centering
	\caption{Priority model n 16, m 9, p 10,  t5e5, unit MiB, 2 kernels}
	\label{pmod_mem}
	\begin{tabular}{| l | l | l |}
		\hline
		DX &DXCon &DXOpt\\ \hline
		35 & 58 &69\\ \hline
	\end{tabular}
\end{table}
